\documentclass [9pt] {beamer}
\usepackage[latin1]{inputenc}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\usetheme{Copenhagen}

\title{Diana Ross Wig Track}
\subtitle{Allison Semmes (Diana Ross)}

\author{Paige Howie}
\date{April 1, 2013}
\institute {Oriental Theater\\Chicago, IL}
\begin{document}

\frame{\titlepage}

\section{Pre-show}
\subsection{Pre Sets-Continuity Hour}
   \frame{
   \textbf{Pre Set the following wigs at the following locations:}
   \begin{itemize}
     \item Nook: 3 Ed Sullivan wigs (Allison, Ensemble Actor 1, Ensemble Actor 2), Copa 1 and TCB
     \item Prop Room: Paris Twist, Manchester and Wide Bubble
     \item Lift: Reach Out
     \item S.L Mirror: Motown 25
   \end{itemize}
  
  \begin{center} 
  \textbf{*GENERAL NOTES*}
  \\THE MAJORITY OF ALL CHANGES ARE QUICK CHANGES!
  \end{center} 
 
  -Make sure Allison has a water bottle available at every change.  \\(Sometimes she may grab for it out of your apron.)  \\-Make sure you have coconut oil.  \\-Allison will look for your hand for support during her changes.    \\-You will follow Allison and her dresser Richard for the entire track.  \\-The only wig that gets pinned at the nape is her Motown 25 wig.  
  
    
    }
 
 \subsection{Half Hour}
   \frame{
   Go to Allison's dressing room with WIG 1 YOUNG DIANA.  
   \\Pin 2 mic pics onto her nape.  Help her tape her in ears.  
   \\She will wear a total of 3 wig caps applied in the following order: 
   \begin{itemize}
   \item regular black
   \item the mics will go on top of the black cap and a mesh cap goes on top of the mics  
   \item a regular black cap is applied over the mesh. 
   \end{itemize}
    Pin on Wig 1 with two large pins on top and a small pin on each side.  Make sure her bobby pins are placed correctly.  
   
   }
   
\end{document}
